DOM Review Stats and Figures

### 2024-09-23 Analysis/Analysis.qmd
Clear archived files

```{r load packages}
#| include: false
library(tidyverse)
library(patchwork)
library(sf)
library(readxl)
```

@@

```{r Taxa bar plot}
focalTaxaPlot <- sheet_FocalTaxa |>
  mutate(Status = case_when(Status %in% c("CR", "EN", "NT", "VU", "Threatened_Other") ~ "Threatened",
                            Status == "NA" ~ "Multiple species",
                            Status == "Invasive" ~ "Invasive",
                            Status == "LC" ~ "Stable")) |>
  mutate(Status = fct(Status, levels = c("Multiple species", "Invasive",
                                         "Stable", "Threatened"))) |>
  summarise(Articles = n(), .by = c(`Taxa keywords`, Status)) |>
  select(Articles, Taxa = `Taxa keywords`, Status) |>
  mutate(Taxa = case_when(Taxa == "NA" ~ "Other", .default = Taxa)) |>
  mutate(Taxa = fct(Taxa, levels = rev(c("Bird", "Mammal", "Herptile",
                                         "Fish", "Invertebrate", "Other")))) |>

  ggplot() +
  geom_col(aes(x = Articles, y = Taxa, fill = Status)) +
  scale_fill_manual("", values = c("gray40", "plum4", "aquamarine4", "firebrick4")) +
  labs(x = "Articles", y = "") +
  theme(panel.grid = element_blank(),
        #legend.position = "top",
        legend.text = element_text(size = 20), axis.text = element_text(size = 21),
        axis.title = element_text(size = 19), axis.ticks.y = element_blank(),
        panel.background = element_rect(fill='transparent', color = NA),
        plot.background = element_rect(fill='transparent', color = NA),
        legend.background = element_rect(fill = 'transparent', color = NA))
focalTaxaPlot

ggsave("Manuscript/Figures/TaxaPlot.png",
       focalTaxaPlot, width = 10, height = 4, bg='transparent')

@@

@@

  ggplot() +
  geom_col(aes(x = Year, y = Articles, fill = Group), colour = "white") +
  scale_fill_manual("",
                    limits = c("YES", "EstRemaining"),
                    labels = c("Included articles", 
                               "Estimated qualifying articles"),
                    values = c("aquamarine4", "gray70")) +
  labs(x = "", y = "Number of articles") +
  theme(panel.grid.major.x = element_blank(),
        legend.position = "top", axis.text = element_text(size = 12),
        axis.title = element_text(size = 12), legend.text = element_text(size = 12))
coveragePlot
ggsave(plot = coveragePlot, "Manuscript/Figures/CoveragePlot.jpeg",
       width = 8, height = 4)
```

@@

  ggplot() +
  geom_sf(data = countries_shp, colour = "gray90", fill = "gray80") +
  geom_sf(shape = 21,fill = "aquamarine4", colour = "white", alpha = 0.7, size = 2.5) +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
studyArea_Map
ggsave(plot = studyArea_Map, "Manuscript/Figures/StudiesMap.png")
```

@@

  ggplot() +
  geom_col(aes(x = Size, y = Articles),
           fill = "aquamarine4") +
  labs(x = "", y = "") +
  scale_x_discrete(labels = c("0-1", "1-10", "10-100",
                              "100-\n1000", "1000-\n10000",
                              "10000-\n100000", "100000-\n1000000",
                              "1000000+")) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 20,
                                   angle = 90,
                                   vjust = 0.5, hjust = 1),
        axis.text.y = element_blank(), axis.ticks = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
studyAreaPlot

ggsave("Manuscript/Figures/StudyAreaPlot.png",
       studyAreaPlot, width = 8, height = 4, bg='transparent') 
```

@@

@@

  ggplot() +
  geom_histogram(aes(y = StudyMonths), 
                 binwidth = 0.2, fill = "aquamarine4", colour = "white") +
  geom_hline(aes(yintercept = median(StudyMonths)), 
             colour = "goldenrod3", linetype = 2, linewidth = 2) +
  labs(y = "", x = "") +
  scale_y_continuous(transform = "log10",
                     limits = c(0.5,725),
                     breaks = c(1, 6, 12, 60, 
                                120, 240, 480, 720), 
                     labels = c("1 month", "6 months", "1 year", "5 years", 
                                "10 years", "20 years", "40 years", "60 Years")) +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        axis.text.y = element_text(size = 23),
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
studyDurationPlot
ggsave(plot = studyDurationPlot, filename = "Manuscript/Figures/Duration.png",
       height = 8, width = 4)
```

@@

```{r plot site quantity}
siteQuantityPlot <- sheet_DataCollection |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  ggplot() +
  geom_histogram(aes(y = `Site quantity`),
                 binwidth = 0.25, fill = "aquamarine4", colour = "white") +
  geom_hline(aes(yintercept = median(`Site quantity`, na.rm = TRUE)), 
             colour = "goldenrod3", linetype = 2, linewidth = 2) +
  scale_y_continuous(transform = "log10",
                     limits = c(5, 10000),
                     breaks = c(10, 25, 50, 100, 250, 500,
                                1000, 2500, 5000, 10000)) +
  scale_x_continuous(expand = c(0,0)) +
  labs(x = "", y = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        axis.text.y = element_text(size = 23),
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
siteQuantityPlot
ggsave(plot = siteQuantityPlot, filename = "Manuscript/Figures/Sites.png",
       height = 8, width = 4)
```

@@

covParamPlot
ggsave(plot = covParamPlot, filename = "Manuscript/Figures/CovParamPlot.jpeg",
       width = 8, height = 4)
```

@@

```{r Covariate table}
# Covariate level summaries ------------------------------------------------
# Extract details for each covariate and get parameter counts
covariate_details <- sheet_Covariates |>
  separate_longer_delim(Covariates, delim = ", ") |>
  separate_wider_delim(Covariates, delim = "_", 
                       names = c("Covariate", "Variation", 
                                 "Observation", "Relation"),
                       too_few = "align_start") |>
  separate_wider_delim(Covariate, delim = "-",
                       names = c("Category", "Covariate"),
                       too_few = "align_start") |>
  mutate(n_overall = length(unique(`Review ID`))) |>
  mutate(n_param = length(unique(`Review ID`)), 
         .by = `Parameter type`) |>
  mutate(Dynamic = case_when(Variation %in% c("SE", "SISE", "SU") ~ TRUE,
                             .default = FALSE),
         DirectObs = case_when(Observation == "D" ~ TRUE, 
                               .default = FALSE),
         Nonlinear = case_when(Relation %in% c("N", "B") ~ TRUE,
                               .default = FALSE),
         Interaction = case_when(Relation %in% c("I", "B") ~ TRUE,
                                 .default = FALSE)) |>
  filter(!is.na(Covariate))

@@

write_csv(fullCovariateSummary, "Manuscript/Figures/CovariateTable.csv")
```

@@

  ggplot() +
  geom_col(aes(x = `Year Strata`, y = PropArticles, fill = Objective),
           position = "dodge", colour = "white") + 
  scale_fill_manual("",
                    values = c("plum4", "cadetblue3", "aquamarine3",
                               "aquamarine4", "goldenrod2", "goldenrod3")) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80),
                     limits = c(0, 80),
                     labels = c("0%", "20%", "40%", "60%", "80%")) +
  labs(y = "Percentage of studies\nwith objective", x = "") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.text = element_text(size = 15),
        axis.text = element_text(size = 15), axis.title = element_text(size = 15),
        legend.position = "bottom", strip.background = element_blank(),
        strip.text = element_blank()) +
  facet_grid(cols = vars(Strata),
             scales = "free_x", space = "free_x", drop = TRUE)
objectiveTrendPlot
ggsave(plot = objectiveTrendPlot, "Manuscript/Figures/ObjectiveTrend.jpeg",
       width = 8, height = 4)
```

@@

  ggplot(aes(x = Objective, y = CovsPerParam, 
             fill = Objective, colour = Objective)) +
  geom_boxplot(colour = "gray50", alpha = 0.6) +
  geom_jitter(alpha = 0.6, width = 0.1) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10),
                     labels = c("0", "2", "4", "6", "8", "10+")) +
  scale_fill_manual(limits = c("Any\nObjective", "Demonstrate\nmethods", 
                               "Observe\ntrends", "Identify\ndrivers", 
                               "Test\nrelationships", "Predict\nspatially",
                               "Predict\ntemporally"),
                    values = c("gray60", "plum4", "cadetblue3", "aquamarine3",
                               "aquamarine4", "goldenrod2", "goldenrod3")) +
  scale_colour_manual(limits = c("Any\nObjective", "Demonstrate\nmethods", 
                                 "Observe\ntrends", "Identify\ndrivers", 
                                 "Test\nrelationships", "Predict\nspatially",
                                 "Predict\ntemporally"),
                      values = c("gray60", "plum4", "cadetblue3", "aquamarine3",
                                 "aquamarine4", "goldenrod2", "goldenrod3")) +
  labs(x = "", y = "Number of covariates\nconsidered per parameter") +
  facet_grid(cols = vars(facet), scales = "free_x", space = "free_x") +
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
        legend.text = element_text(size = 15), axis.text = element_text(size = 13),
        axis.title = element_text(size = 15), strip.background = element_blank(),
        strip.text = element_blank()) 
objectiveCovariatePlot
ggsave(plot = objectiveCovariatePlot, "Manuscript/Figures/ObjectiveCovariates.jpeg",
       width = 8, height = 4)
```

@@

ggsave(plot = stackedObjectivePlot, "Manuscript/Figures/ObjectiveFigure.jpeg",
       width = 12, height = 8)
```

@@

write_csv(modelling_summary, "Manuscript/Figures/ModellingSummary.csv")
```

>>>>

```{r load packages}
#| include: false
library(tidyverse)
library(patchwork)
library(sf)
library(readxl)
library(ggtext)
```

@@

```{r Taxa bar plot}
focalTaxaPlot <- sheet_FocalTaxa |>
  mutate(Status = case_when(Status %in% c("CR", "EN", "NT", "VU", "Threatened_Other") ~ "Threatened",
                            Status == "NA" ~ "Multiple species",
                            Status == "Invasive" ~ "Invasive",
                            Status == "LC" ~ "Stable")) |>
  mutate(Status = fct(Status, levels = c("Multiple species", "Invasive",
                                         "Stable", "Threatened"))) |>
  summarise(Articles = n(), .by = c(`Taxa keywords`, Status)) |>
  select(Articles, Taxa = `Taxa keywords`, Status) |>
  mutate(Taxa = case_when(Taxa %in% c("NA", "Fish") ~ "Other", .default = Taxa)) |>
  mutate(Taxa = fct(Taxa, levels = rev(c("Bird", "Mammal", "Herptile",
                                        "Invertebrate", "Other")))) |>

  ggplot() +
  geom_col(aes(x = Articles, y = Taxa, fill = Status)) +
  scale_fill_manual("", values = c("gray70", "plum4", "aquamarine4", "goldenrod2")) +
  labs(x = "Articles", y = "") +
  theme(panel.grid = element_blank(),
        #legend.position = "top",
        legend.text = element_text(size = 20), axis.text = element_text(size = 21),
        axis.title = element_text(size = 19), axis.ticks.y = element_blank(),
        panel.background = element_rect(fill='transparent', color = NA),
        plot.background = element_rect(fill='transparent', color = NA),
        legend.background = element_rect(fill = 'transparent', color = NA))
focalTaxaPlot

ggsave("Figures/TaxaPlot.png",
       focalTaxaPlot, width = 10, height = 4, bg='transparent')

sheet_FocalTaxa |>
  select(`Review ID`, `Multispecies method`) |>
  distinct() |>
  summarise(Articles = n(), .by = `Multispecies method`)
```

@@

```{r strata hit rates}
sheet_ArticleData |>
  pull(`Review ID`) |>
  length()

randomisationSheets |>
  summarise(N = n(), .by = c(Year, Strata, Included)) |>
  pivot_wider(names_from = Included, values_from = N, values_fill = 0) |>
  summarise(HitRate = sum(YES)/(sum(NO)+sum(YES)),
            .by = Strata)

  randomisationSheets |>
  summarise(N = n(), .by = c(Year, Strata, Included)) |>
  pivot_wider(names_from = Included, values_from = N, values_fill = 0) |>
  mutate(HitRate = sum(YES)/(sum(NO)+sum(YES)),
         .by = Strata) |>
  summarise(HitRate = mean(HitRate), `NA` = sum(`NA`),
            .by = Year) |>
  mutate(EstRemaining = `NA`*HitRate) |>
  summarise(`NA` = sum(`NA`), EstRemaining = sum(EstRemaining))
```

@@

  ggplot() +
  geom_col(aes(x = Year, y = Articles, fill = Group), colour = "white") +
  scale_fill_manual("",
                    limits = c("YES", "EstRemaining"),
                    labels = c("Included articles", 
                               "Estimated qualifying articles"),
                    values = c("aquamarine4", "gray70")) +
  scale_y_continuous(expand = c(0,0), limits = c(0, 65)) +
  labs(x = "", y = "Number of articles") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "bottom", axis.text = element_text(size = 12),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.title = element_text(size = 12), legend.text = element_text(size = 12),
        strip.text.x = element_text(size = 12)) +
  facet_grid(cols = vars(Strata), scales = "free_x", switch = "x")
coveragePlot
ggsave(plot = coveragePlot, "Figures/CoveragePlot.jpeg",
       width = 8, height = 4)
```

@@

  ggplot() +
  geom_sf(data = countries_shp, colour = "gray90", fill = "gray80") +
  geom_sf(shape = 21,fill = "aquamarine4", colour = "white", alpha = 0.7, size = 2.5) +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
studyArea_Map
ggsave(plot = studyArea_Map, "Figures/StudiesMap.png")

sheet_StudyArea |>
  select(`Review ID`, Country) |>
  separate_longer_delim(Country, ", ") |>
  distinct() |>
  summarise(Articles = n(), .by = Country) |>
  arrange(-Articles)

@@

  ggplot() +
  geom_col(aes(x = Size, y = Articles),
           fill = "aquamarine4", colour = "white",
           width = 1, linewidth = 2) +
  labs(x = "", y = "") +
  scale_x_discrete(labels = c("< 1", "1 - 10", "10 - 10<sup>2</sup>",
                              "10<sup>2</sup> - 10<sup>3</sup>",
                              "10<sup>3</sup> - 10<sup>4</sup>",
                              "10<sup>4</sup> - 10<sup>5</sup>",
                              "10<sup>5</sup> - 10<sup>6</sup>",
                              "10<sup>6</sup> +")) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_markdown(size = 20, angle = 90,
                                       vjust = 0.5, hjust = 1),
        axis.text.y = element_blank(), axis.ticks = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
studyAreaPlot

ggsave("Figures/StudyAreaPlot.png",
       studyAreaPlot, width = 7, height = 4, bg='transparent') 
```

@@

survey methods

```{r survey methods}
sheet_DataCollection |>
  select(`Review ID`, `Capture method`) |>
  separate_longer_delim(`Capture method`, ", ") |>
  distinct() |>
  summarise(Articles = n(), .by = `Capture method`)

sheet_DataCollection |>
  select(`Review ID`, Citizen) |>
  distinct() |>
  summarise(Articles = n(), .by = Citizen)

@@

  ggplot() +
  geom_histogram(aes(x = StudyMonths), 
                 binwidth = 0.2, fill = "aquamarine4", colour = "white",
                 linewidth = 2) +
  geom_vline(aes(xintercept = median(StudyMonths)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  labs(x = "", y = "Study\nduration") +
  scale_x_continuous(transform = "log10",
                     limits = c(0.5,725),
                     breaks = c(1, 6, 12, 60, 
                                120, 240, 480), 
                     labels = c("1 month", "6 months", "1 year", "5 years", 
                                "10 years", "20 years", "40 years"),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        axis.text.x = element_text(size = 23, angle = 90,
                                   vjust = 0.5, hjust = 1),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.line.x = element_line(), 
        axis.title.y = element_text(size = 35, colour = "aquamarine4"))
studyDurationPlot
ggsave(plot = studyDurationPlot, filename = "Figures/Duration.png",
       height = 3, width = 12)

sheet_DataCollection |>
  mutate(StartDay = as.numeric(as.Date(`Start month`)),
         EndDay = as.numeric(as.Date(`End month`))) |>
  mutate(StudyDuration = EndDay - StartDay) |>
  mutate(StudyMonths = (StudyDuration/30)) |>
  mutate(StudyMonths = case_when(StudyMonths == 0 ~ 1,
                                 .default = StudyMonths)) |>
  summarise(StudyMonths = mean(StudyMonths, na.rm = TRUE),
            .by = `Review ID`) |>
  pull(StudyMonths) |>
  median(na.rm = TRUE)
```

@@

```{r plot site quantity}
siteQuantityPlot <- sheet_DataCollection |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  ggplot() +
  geom_histogram(aes(x = `Site quantity`),
                 binwidth = 0.25, fill = "aquamarine4", colour = "white",
                 linewidth = 2) +
  geom_vline(aes(xintercept = median(`Site quantity`, na.rm = TRUE)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  scale_x_continuous(transform = "log10",
                     limits = c(5, 10000),
                     breaks = c(10, 25, 50, 100, 250, 500,
                                1000, 2500, 5000),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  labs(y = "Site\nquantity", x = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        axis.text.x = element_text(size = 23, angle = 90,
                                   vjust = 0.5, hjust = 1),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.line.x = element_line(), 
        axis.title.y = element_text(size = 35, colour = "aquamarine4"))
siteQuantityPlot
ggsave(plot = siteQuantityPlot, filename = "Figures/Sites.png",
       height = 3, width = 12)

sheet_DataCollection |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  summarise(Sites = mean(`Site quantity`, na.rm = TRUE), 
            .by = `Review ID`) |>
  pull(Sites) |>
  median(na.rm = TRUE)
```

Combine sites and durations

```{r site and duration combination}
combinedStudyScale <- studyDurationPlot / siteQuantityPlot
combinedStudyScale <- combinedStudyScale +
  theme(panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
ggsave(plot = combinedStudyScale, filename = "Figures/StudyScale.png",
       height = 6, width = 12)
```

@@

covParamPlot
ggsave(plot = covParamPlot, filename = "Figures/CovParamPlot.jpeg",
       width = 8, height = 4)
```

@@

```{r Covariate table}
# Covariate level summaries ------------------------------------------------
# Extract details for each covariate and get parameter counts
covariate_details <- sheet_Covariates |>
  separate_longer_delim(Covariates, delim = ", ") |>
  separate_wider_delim(Covariates, delim = "_", 
                       names = c("Covariate", "Variation", 
                                 "Observation", "Relation"),
                       too_few = "align_start") |>
  separate_wider_delim(Covariate, delim = "-",
                       names = c("Category", "Covariate"),
                       too_few = "align_start") |>
  mutate(Covariate = case_when(Covariate == "OTHER" & Category == "E" ~ "OTHER-E",
                               Covariate == "OTHER" & Category == "S" ~ "OTHER-S",
                               Covariate %in% c("HABT", "HABA", "LACO") ~ "HABT",
                               Covariate %in% c("CLWE", "DISA", "DIST") ~ "CLWE",
                               Covariate %in% c("SPAT", "GEOM", "CONN") ~ "SPAT",
                               Covariate %in% c("TOPO", "HYDR") ~ "TOPO",
                               Covariate %in% c("ANTH", "AGRI", "PROT") ~ "ANTH",
                               .default = Covariate)) |>
  mutate(n_overall = length(unique(`Review ID`))) |>
  mutate(n_param = length(unique(`Review ID`)), 
         .by = `Parameter type`) |>
  mutate(Dynamic = case_when(Variation %in% c("SE", "SISE", "SU") ~ TRUE,
                             .default = FALSE),
         DirectObs = case_when(Observation == "D" ~ TRUE, 
                               .default = FALSE),
         Nonlinear = case_when(Relation %in% c("N", "B") ~ TRUE,
                               .default = FALSE),
         Interaction = case_when(Relation %in% c("I", "B") ~ TRUE,
                                 .default = FALSE)) |>
  filter(!is.na(Covariate))

@@

write_csv(fullCovariateSummary, "Figures/CovariateTable.csv")
```

@@

  ggplot() +
  geom_col(aes(x = `Year Strata`, y = PropArticles, fill = Objective),
           position = "dodge", colour = "white") + 
  scale_fill_manual("",
                    values = c("plum4", "cadetblue3", "aquamarine3",
                               "aquamarine4", "goldenrod2", "goldenrod3")) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80),
                     limits = c(0, 80),
                     labels = c("0%", "20%", "40%", "60%", "80%")) +
  labs(y = "Percentage of studies\nwith objective", x = "") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.text = element_text(size = 15),
        axis.text = element_text(size = 15), axis.title = element_text(size = 15),
        legend.position = "bottom", strip.background = element_blank(),
        strip.text = element_blank()) +
  facet_grid(cols = vars(Strata),
             scales = "free_x", space = "free_x", drop = TRUE)
objectiveTrendPlot
ggsave(plot = objectiveTrendPlot, "Figures/ObjectiveTrend.jpeg",
       width = 8, height = 4)
```

@@

  ggplot(aes(x = Objective, y = CovsPerParam, 
             fill = Objective, colour = Objective)) +
  geom_boxplot(colour = "gray50", alpha = 0.6) +
  geom_jitter(alpha = 0.6, width = 0.1) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10),
                     labels = c("0", "2", "4", "6", "8", "10+")) +
  scale_fill_manual(limits = c("Any\nObjective", "Demonstrate\nmethods", 
                               "Observe\ntrends", "Identify\ndrivers", 
                               "Test\nrelationships", "Predict\nspatially",
                               "Predict\ntemporally"),
                    values = c("gray60", "plum4", "cadetblue3", "aquamarine3",
                               "aquamarine4", "goldenrod2", "goldenrod3")) +
  scale_colour_manual(limits = c("Any\nObjective", "Demonstrate\nmethods", 
                                 "Observe\ntrends", "Identify\ndrivers", 
                                 "Test\nrelationships", "Predict\nspatially",
                                 "Predict\ntemporally"),
                      values = c("gray60", "plum4", "cadetblue3", "aquamarine3",
                                 "aquamarine4", "goldenrod2", "goldenrod3")) +
  labs(x = "", y = "Number of covariates\nconsidered per parameter") +
  facet_grid(cols = vars(facet), scales = "free_x", space = "free_x") +
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
        legend.text = element_text(size = 15), axis.text = element_text(size = 13),
        axis.title = element_text(size = 15), strip.background = element_blank(),
        strip.text = element_blank()) 
objectiveCovariatePlot
ggsave(plot = objectiveCovariatePlot, "Figures/ObjectiveCovariates.jpeg",
       width = 8, height = 4)
```

@@

ggsave(plot = stackedObjectivePlot, "Figures/ObjectiveFigure.jpeg",
       width = 12, height = 8)
```

@@

write_csv(modelling_summary, "Figures/ModellingSummary.csv")
```
